```{r global_options, include=FALSE}
knitr::opts_chunk$set(fig.width=12, fig.height=8, fig.path='Figs/',
                      echo=FALSE, warning=FALSE, message=FALSE)
```

Red Wine Exploration by Darren
========================================================

```{r echo=FALSE, message=FALSE, warning=FALSE, packages}
# Load all of the packages that you end up using in your analysis in this code
# chunk.

# Notice that the parameter "echo" was set to FALSE for this code chunk. This
# prevents the code from displaying in the knitted HTML output. You should set
# echo=FALSE for all code chunks in your file, unless it makes sense for your
# report to show the code that generated a particular plot.

# The other parameters for "message" and "warning" should also be set to FALSE
# for other code chunks once you have verified that each plot comes out as you
# want it to. This will clean up the flow of your report.

library(ggplot2)
library(reshape2)
library(corrplot)
library(gridExtra)
```

```{r echo=FALSE, Load_the_Data}
# Load the Data
redWineData = read.csv('wineQualityReds.csv')
```

# Univariate Plots Section
Let's try to understing the data structure first.
```{r echo=FALSE, Univariate_Plots}
# Dimensions of the data
dim(redWineData)

# Pummary of the data set
summary(redWineData)
str(redWineData)

# Print out a few records to get a clear idea of the data structure
head(redWineData)
```

Before we do any analysis, we would like to take a look on the data to see if
there are any data with a missing values or infinite values that we need to
take care in analysis process.

```{r echo=FALSE}
apply(redWineData, 2, function(x) any(is.na(x)))
apply(redWineData, 2, function(x) any(is.infinite(x)))
```

Luckily, there are no records that we need to take special care of missing
fields or inifinte values.

Our data consist of 1599 observations, with 13 variables. As we want to
ultimately find out the relationship between quality and other variable, let's
take a look at the quality distribution first.

```{r echo=FALSE}
# Create helper function to plot histogram
create_histogram_for_feature <- function(variable, binwidth = 0.01) {
  return(ggplot(aes_string(x = variable), data = redWineData) + 
           geom_histogram(binwidth = binwidth))
}

create_histogram_for_feature('quality', 1)
```

As total.sulfur.dioxide is sum of free and bound sulfur dioxide, I would like to
add a field of bound forms of SO2 to see if there are any use in the upcoming
analysis.

```{r echo=FALSE}
redWineData['bound.sulfur.dioxide'] = redWineData['total.sulfur.dioxide'] -
  redWineData['free.sulfur.dioxide']
```

Also, we will plot a histogram for all the variables to see, trying to pinpoint
some interesting fields that we should take a closer look.sum(is.na(z$Ozone))

```{r echo=FALSE}
ggplot(data = melt(redWineData), mapping = aes(x = value)) + 
  geom_histogram(bins = 10) +
  facet_wrap(~variable, scales = 'free_x')
```

from the histogram that we plotted, we can see that there are a number of fields
either having rather evenly distributed values across the range or not much
variation in values at all. To confirm the latter, we will calculate the
standard deviation of each of the columns.

```{r echo=FALSE}
apply(redWineData, 2, sd)
```

As we can see, density, chlorides are having a very small variation, so we will
just ignore them in the upcoming analysis, suspecting that they are not
contributing much to the quality. The actual correlation of this will leave to
bivariate analysis.

We would also like to know more about each of the interested fields(those 
mentioned in the dataset description that would affect the taste, i.e. volatile
acidity, citric acid, residual sugar, free sulfur dioxide), let's try to plot 
the interested fields individually.

```{r echo=FALSE}
create_histogram_for_feature('volatile.acidity', 0.1)
create_histogram_for_feature('citric.acid', 0.1)
create_histogram_for_feature('residual.sugar', 0.1)
create_histogram_for_feature('free.sulfur.dioxide', 1)
```

The volatile acidity graph looks distributed normally. Citric acid seems to have a pretty uniform distribution across different level. The residual suagr one and the free.sulfur.dioxide one looks skewed. Let's try to plot them in log scale and see if there are anything interesting.

```{r echo=FALSE}
create_histogram_for_feature('residual.sugar', 0.05) + 
  scale_x_log10()
create_histogram_for_feature('free.sulfur.dioxide', 0.1) + 
  scale_x_log10()
```

We can see that free.sulfur.dioxide one looks much more normal after 
transforming into log scale. I would say we should analyse free.sulfur.dioxide 
in log scale going forward.

For residual.sugar, actually they are having a similar distribution as the 
orginal scaled one. In fact, if we look at the original one closely, we can see 
that the graph is not that skewed. It looks skewed just because there are some 
outliers on the right side. I guess those are the specially fruit favoured wine.

With this findings, it would also make sense for us to plot histogram for total 
and bound sulfur distribution as well.
```{r echo=FALSE}
create_histogram_for_feature('total.sulfur.dioxide', 1)
create_histogram_for_feature('bound.sulfur.dioxide', 1)
```
Both are also very skewed. Let's try to plot them in log scale.

```{r echo=FALSE}
create_histogram_for_feature('total.sulfur.dioxide', 0.1) + 
  scale_x_log10()
create_histogram_for_feature('bound.sulfur.dioxide', 0.1) + 
  scale_x_log10()
```

Both look distributed normally now. So here, we will create a new field for log-scaled free.sulfur.dioxide, bound.sulfur.dioxide and total.sulfur.dioxide.

```{r echo=FALSE}
redWineData['free.sulfur.dioxide.log'] = log(redWineData['free.sulfur.dioxide'])
redWineData['bound.sulfur.dioxide.log'] = log(redWineData['bound.sulfur.dioxide'])
redWineData['total.sulfur.dioxide.log'] = log(redWineData['total.sulfur.dioxide'])
```

# Univariate Analysis

### What is the structure of your dataset?
There are 1,599 red wine records in the dataset with 11 features(fixed.acidity,
volatile.acidity, citric.acid, residual.sugar, chlorides, free.sulfur.dioxide,
total.sulfur.dioxide, density, pH, sulphates, alcohol) and 1 output variable
(quality). 

All of the features are numbers, while quality are integers.

Other observations:
1. quality ranges from 3-8, without extreme value from 0-2 or 9-10.
2. quality is following a normal distribution
3. 75% of observations are having a chlorides level < 0.09, and surprisingly
there are samples with almost 7 times of this value

### What is/are the main feature(s) of interest in your dataset?
Based on the description from the dataset and some research, I think volatile
acidity, citric acid, residual sugar, free sulfur dioxide would be the main
features to predict quality.

### What other features in the dataset do you think will help support your \
investigation into your feature(s) of interest?
There are some other features that I suspect that fixed acidity/pH are highly
related or even representing very similar trends. As there are impacting the
taste, I would suspect that there will contribute partly to the quality score.

Also sulphates and the three SO2 fields should be correlated. We will perform
correlation analysis in the next part to confirm these relationships.


### Did you create any new variables from existing variables in the dataset?
I created a new field for bound form of sulfur dioxide, which is
(total.sulfur.dioxide - free.sulfur.dioxide). While we don't know if bounded
form of SO2 would be of interest or correlation with the quality, we could do
some correlation analysis in the next section.

### Of the features you investigated, were there any unusual distributions? \
Did you perform any operations on the data to tidy, adjust, or change the form \
of the data? If so, why did you do this?

Luckily, there are no missing values or infinite values in our dataset.

As we found that sulfur.dioxide fields seems skewed and we tried to plot them 
with log scale. With log-scaled, we found that they are now distributed more 
normally. So we also created log-scaled version of these fields.

However, I do found that density and chloride field is having very small
variation, which I would exclude them from further analysis as I doubt if that
small variation are contributing to the difference in taste.




# Bivariate Plots Section

Firstly, we will calculate the correlation matrix before we go ahead on more
detailed analysis.

```{r echo=FALSE, Bivariate_Plots}
correlations = cor(redWineData, method = "pearson")
corrplot(correlations, method="color")
```

Let's look at the guess we made in part 1, fixed acidity/pH are highly related
also for sulphates and the three SO2 fields. Turns out part of our guess is
correct, fixed acidity and pH does have a very strong negative correlation.
However there are no significant correlations with the sulplates fields with the
other 3 sulfur related fields.

Another focus was other high correlations between features. We found that there
are high positive correlations with fixed.acidity and density/citric acid. Also,
citric.acid is also fairly negatively correlated with volatile.acid and pH.
Citric.acid is also fairly positive related with fixed.acidity.

While sulplates are not particularly correlated with the three sulfur fields,
the three sulfur fields(both log and non-log scaled version) are highly 
correlated themselves.

So to conclude, I would drop a number of fields from further analysis, i.e. I
will take total.sulfur.dioxide.log to represent all three sulfur fields, and pH 
to represent all acid-related fields).

To be more solid about these integrated fields, we will plot graphs of sulfur
fields and acidic fields to take a look at their trend.

```{r echo=FALSE}
# Create helper function for creating scatter plot with smoothing line
create_scatter_plot <- function(feature_x, feature_y) {
  return (ggplot(aes_string(x = feature_x, y = feature_y), data=redWineData) +
  geom_point(alpha = 1/10) +
  geom_smooth(alpha=.2, size=1))
}

sulfurP1 <- create_scatter_plot('free.sulfur.dioxide.log', 'total.sulfur.dioxide.log')
sulfurP2 <- create_scatter_plot('bound.sulfur.dioxide.log', 'total.sulfur.dioxide.log')

grid.arrange(sulfurP1, sulfurP2)
```

These two graphs confirmed our view that total.sulfur.dioxide.log can conclude both
free and bound sulfur dioxide features.

```{r echo=FALSE}
acidP1 <- create_scatter_plot('fixed.acidity', 'pH')
acidP2 <- create_scatter_plot('volatile.acidity', 'pH')
acidP3 <- create_scatter_plot('citric.acid', 'pH')

grid.arrange(acidP1, acidP2, acidP3)
```

These three plots also confirmed our views that fixed.acidity and citric.acid
can be concluded by pH feature. While volatile.acidity showed a positive
correlation with pH, that might actually referring to the higher volatile
acidity, the lower the fixed acidity. But no matter what, pH would be a nice
indicator of the acidity of the wine. If we are looking more closely with the
correlation between pH and other fields, we would not be surprised that it also
have a minor correlation with the acidic sulphur dioxide fields.

We will conclude our first part of bivariate analysis for combining related
features. Next, we will move on to the next part for finding features that are
critical for predicting the quality of wine.

We will now look at the correlation between quality and other features.

We would immediately notice the strong negative relationship between quality and
volatile.acidity. However, there are not strong correlation between pH and
quality. Thus, the total acidity indication concept(pH) we came up in the last
part is not really useful in predicting quality. In turn, we should put a lesser
weight on other acidic features but focusing on volatile acidity.

Also, it's easy to spot that alcohol level is having a strong positive
relationship with quality.

Therefore, in the next part, volatile.acidity and alcohol will be the main
features that we are looking to predict the wine quality.

According to the dataset description, there are 2 fields particularly important
in terms of taste or favor, which are citric.acid and residual.sugar. One is
providing a fresh taste and another is providing a sweet taste. Surprisingly,
sweet taste (represented by residual.sugar) doesn't really correlated to quality
while freshness (represented by citric.acid) have a weak effect on quality.

We will now plot the scatter plot for our two main features of interests and one
side feature for citric acid.

```{r echo=FALSE}
qualityP1 <- create_scatter_plot('alcohol', 'quality')
qualityP2 <- create_scatter_plot('volatile.acidity', 'quality')
qualityP3 <- create_scatter_plot('citric.acid', 'quality')

grid.arrange(qualityP1, qualityP2, qualityP3)
```
 
# Bivariate Analysis

### Talk about some of the relationships you observed in this part of the \
investigation. How did the feature(s) of interest vary with other features in \
the dataset?

There are two part of bivariate analysis. First part concerns the duplication or
redundance fields.
We concluded that pH field can act as an integrated indicator of multiple acidic
fields including fixed.acidity, volatile.acidity and citric.acid. However, this
pH indicator doesn't really correlate with the quality variable so we will put
it aside for further investigation.

We also found that the three sulphur fields can be concluded by the
total.sulfur.dioxide.log field but this field also have a weak correlation with 
the quality variable.


### Did you observe any interesting relationships between the other features \
(not the main feature(s) of interest)?
While we have selected volatile acidity, citric acid, residual sugar, free
sulfur dioxide as main features to investigate in univariable analysis, we will
need to change our main features into alcohol and volatile acidity after our
analysis of correlation between quality and other fields.

Only alcohol and volatile acidity is showing significat relationship with 
quality in correlation analysis.

Of couse we also found other interesting relationship like density is strongly
correlated with fixed.acidity but negatively correlated with the alcohol level. 
After some research, this is due to the fact that alcohol is having a lower 
density than water, while acid is having a higher density than water.

### What was the strongest relationship you found?
The strongest relationship I found is between pH and fixed.acidity. This
actually makes a lot of sense as other acidic features are only in a small
amount which hardly impact the overall pH value. This might also explained why
pH doesn't really predict overall quality of wine as pH is dominated by 
fixed.acidity which most experts didn't considered or feel like a critical 
factor contributing to the quality. In fact, volatile.acidity is the main factor
affecting the quality but it is under-repesented in the pH value.

# Multivariate Plots Section

In this section, we will focus on looking at how to predict quality of the wine.
As we identified the two main fatures alread, we will first plot the graph for 
the 2 main features and quality score.

```{r echo=FALSE, Multivariate_Plots}
redWineData$quality.factor <- as.factor(redWineData$quality)
ggplot(aes(x = alcohol, y = volatile.acidity, color = quality.factor),
       data=redWineData) +
  geom_point() +
  scale_colour_brewer(type = "seq", palette = 2) +
  theme_dark()
```

From the plot above, it is easily seen that all the good quality wine are 
distributed in the lower right part of the graph, indicating that the higher the
alcohol level and the lower the volatile.acidity, the better the quality of the
wine.

We will also try to build a mathematical model of the data making use of the two
main features. and do some predictions on the existing dataset based on the new
model. (Note: we are not separating the data into training set and test set as 
we are not going to do machine learning here. We just want to understand more 
about the dataset and exploration)

```{r echo=FALSE}
model1 = lm(quality ~ alcohol + volatile.acidity, data = redWineData)
summary(model1)

redWineData['predicted'] = fitted(model1)
redWineData['predicted.absError'] <- abs(redWineData['predicted'] -
                                         redWineData['quality'])
summary(redWineData['predicted.absError'])
```

With this simple model, we achieved a mean absolute error of 0.52, which is 
pretty accurate without any advanced machine learning techniques. We might also 
wanted to plot the absolute errors and see if this lower level of mean absolute 
error happened just becuase of biased data.

```{r echo=FALSE}
create_histogram_for_feature('predicted.absError', 0.05)
```

From this plot, we can see that most of the predictions are having a error or 
less than 1. In fact, according to the calculations that we did in the last 
part, more than 75% of predictions are having an error less than 0.73. But it is
also worth mentioned that according to the r^2 value, only 31.7% of the variance
of quality is explanined by this model.

In the bivariaate analysis, we also mentioned than citric.acid could be another 
minor factor to contribute to the model. Let's put that into considerations.

```{r echo=FALSE}
model2 = lm(quality ~ alcohol + volatile.acidity + citric.acid, data = redWineData)
summary(model2)

redWineData['predicted.model2'] = fitted(model1)
redWineData['predicted.model2.absError'] <- abs(redWineData['predicted.model2']
                                                - redWineData['quality'])
summary(redWineData['predicted.model2.absError'])

create_histogram_for_feature('predicted.model2.absError', 0.05)
```

No matter from the stats or the absolute error plot, there are no significant 
improvement after we add citric acid as a factor. So we will stop here and 
settle with the 2 factor models for now. (Note: Either model is not a good model
for predicting quality of red wine as they only explained less than 40% of the 
variance. To have a we could create a better model with machine techniques in 
the future, which is out of the scope of this project)

Before we conclude the multivariate analsis section, we will do a bit more 
analysis on the features to see if there are anything interesting.
A while ago we were interested in using pH to represent all the acidic features,
let's see if that's accurate.


```{r echo=FALSE}
# Create helper function for creating scatter plot without smoothing line
create_scatter_plot_without_line <- function(feature_x, feature_y){
  return (ggplot(aes_string(x = feature_x, y = feature_y,
                               color = 'pH'), data=redWineData) +
            geom_point())
}

acidScatterPlot1 <- create_scatter_plot_without_line('fixed.acidity',
                                                     'volatile.acidity')
acidScatterPlot2 <- create_scatter_plot_without_line('fixed.acidity',
                                                     'citric.acid')
acidScatterPlot3 <- create_scatter_plot_without_line('fixed.acidity',
                                                     'total.sulfur.dioxide.log')

grid.arrange(acidScatterPlot1, acidScatterPlot2, acidScatterPlot3)
```

These two plots confirm that the pH value are dominated by the fixed.acidity and
not really impacted by other acidity values.

Another thing that worth looking into is the sulphates and free.sulfur.dioxide.log, 
which both are helping to preserve the wine by prevents microbial growth and the
ocidation. Is quality impacted by these two factors?

```{r echo=FALSE}
ggplot(aes(x = free.sulfur.dioxide.log, y = sulphates, color = quality.factor),
       data=redWineData) +
  geom_point() +
  scale_colour_brewer(type = "seq", palette = 2) +
  theme_dark()
```

Interestingly, seems there are no relationship between these wine preservative 
and the quality. Maybe the the winemakers would tune the level of perservative 
to a suitable amount which higher level or perservative doesn't meant the wine 
is perserved in a better way.

So what about the level of volatile acidity and the preservatives?

```{r echo=FALSE}
ggplot(aes(x = free.sulfur.dioxide.log, y = sulphates, color = volatile.acidity),
       data=redWineData) +
  geom_point() +
  geom_jitter() +
  scale_color_gradient(low="white", high="red") +
  theme_dark()
```

While there are no obviously trend of between perservatives and volatile 
acidity, but there seems to be a really minor ground of high volatile acidity 
and low value in both sulphates and free.sulfur.dioxide.log level. Let's try to 
create a perservative index by normalizing both perservatives fields and adding 
them up.

```{r echo=FALSE}
redWineData['free.sulfur.dioxide.log.scaled'] =
  scale(redWineData['free.sulfur.dioxide.log'])
redWineData['sulphates.scaled'] = scale(redWineData['sulphates'])

redWineData['perservatives'] = redWineData['free.sulfur.dioxide.log.scaled'] +
  redWineData['sulphates.scaled']

create_scatter_plot('perservatives', 'volatile.acidity') +
  scale_x_continuous(breaks = -10:10)
```

And here come the relationships of perservatives and volatile acidity: 
perservatives does help in perserving the wine by preventing the excess volatile
acidity. However, one it surpassed a critical level(our perservative index of 
around 1), adding more perservative doesn't help in improving the quality or 
taste of the wine. So are sulpates and free.sulfur.dioxide.log complement of each 
other?

```{r echo=FALSE}
create_scatter_plot('free.sulfur.dioxide.log.scaled','sulphates.scaled') +
  scale_x_continuous(breaks = -10:10)
```

From this plot, we don't see any complement relationship between sulphates and 
free.sulfur.dioxide.log. In fact, they don't seem to have any relationships at all.

While a lot of people prefer sweeter taste, let's also look at the relationship 
of citric.acid and residual.sugar
```{r echo=FALSE}
ggplot(aes(x = citric.acid, y = residual.sugar, color = quality.factor),
       data=redWineData) +
  geom_point() +
  scale_colour_brewer(type = "seq", palette = 2) +
  theme_dark()
```

From this plot, it's clear that there are no particular preferences of sweetness
for the experts evaluating these wine.

# Multivariate Analysis

### Talk about some of the relationships you observed in this part of the \
investigation. Were there features that strengthened each other in terms of \
looking at your feature(s) of interest?

There are two chemicals, free sulfur dioxide and sulphates contributing to the 
preservation of the wine but their amount doesn't really impact the quality. 
However, if we are keeping the free sulfur dioxide level as constant, the higher
the sulphates, the better the quality of the wine. But in fact, both factor 
doesn't really contribute to the overall quality of the wine.

I also looked into experts preferences of sweetness of the wine but no 
particular trends were found. Apparently the experts doesn't really have 
preferences of sweetness or taste of freshness of the wine.

### Were there any interesting or surprising interactions between features?

We also looked at relationships of perservatives and volatile.acidity(a critical
determinant of quality). perservatives does help in perserving the wine by 
preventing the excess volatile acidity. However, once it surpassed a critical 
level(our perservative index of around 1), adding more perservative doesn't 
help in improving the quality or taste of the wine.

I also originally thought that the two perservatives features must have some 
kind of relationships, either positive relationships or complement but it seems 
that even we standardized the two perservative feature, they don't seems to have
any relationships.

### OPTIONAL: Did you create any models with your dataset? Discuss the \
strengths and limitations of your model.

I created a linear model based on the two main features that we identified, 
alcohol level and volatile acidity. While the good side of the model is that we 
are able to predict most (>75%) wines' quality score with less than 0.5 
difference comparing to the actual score (given that we are having a integer 
scale). However, the R^2 statistics is showing that only 30% of the quality 
variance is explanined by this model. To have a we could create a better model 
with machine techniques in the future, which is out of the scope of this 
project.


------

# Final Plots and Summary

### Plot One
```{r echo=FALSE, Plot_One, fig.width=10,fig.height=12}
freeSulfurLogPlot <- create_histogram_for_feature('free.sulfur.dioxide', 0.1) + 
  scale_x_log10() +
  ggtitle("Distribution of Free Sulfur Dioxide Level in Log Scale") + 
  xlab("Free Sulfur Dioxide Level in Log Scale(mg/dm^3)") +
  ylab("Count") +
  theme(plot.title = element_text(hjust = 0.5))

boundSulfurLogPlot <- create_histogram_for_feature('bound.sulfur.dioxide', 0.1) + 
  scale_x_log10() +
  ggtitle("Distribution of Bound Sulfur Dioxide Level in Log Scale") + 
  xlab("Bound Sulfur Dioxide Level in Log Scale(mg/dm^3)") +
  ylab("Count") +
  theme(plot.title = element_text(hjust = 0.5))

totalSulfurLogPlot <- create_histogram_for_feature('total.sulfur.dioxide', 0.1) + 
  scale_x_log10() +
  ggtitle("Distribution of Total Sulfur Dioxide Level in Log Scale") + 
  xlab("Total Sulfur Dioxide Level in Log Scale(mg/dm^3)") +
  ylab("Count") +
  theme(plot.title = element_text(hjust = 0.5))

grid.arrange(freeSulfurLogPlot, boundSulfurLogPlot, totalSulfurLogPlot)
```

### Description One
The log-scaled sulfur dioxide plots represent the values that we used to analyse
sulfur dioxide level. In univariate analysis, we found that all the three sulfur
dioxide fields are right skewed and we tried to plot a log scaled version of all
these three fields and able to convert them into a more normal distribution. We 
then created three new fields for all three log values for further analysis. 

### Plot Two
```{r echo=FALSE, Plot_Two, fig.width=8,fig.height=12}
acidScatterPlot1 <- create_scatter_plot_without_line('fixed.acidity',
                                                     'volatile.acidity') +
  ggtitle("Scatter Plot on Volatile Acidity and Fixed Acidity,\
          Colored by pH Value") + 
  xlab("Fixed Acidity Level (g/dm^3)") +
  ylab("Volatile Acidity (g/dm^3)") +
  theme(plot.title = element_text(hjust = 0.5))

acidScatterPlot2 <- create_scatter_plot_without_line('fixed.acidity',
                                                     'citric.acid') +
  ggtitle("Scatter Plot on Citric Acid and Fixed Acidity,\
          Colored by pH Value") + 
  xlab("Fixed Acidity Level (g/dm^3)") +
  ylab("Citric Acid Level (g/dm^3)") +
  theme(plot.title = element_text(hjust = 0.5))

acidScatterPlot3 <- create_scatter_plot_without_line('fixed.acidity',
                                                     'total.sulfur.dioxide.log') +
  ggtitle("Scatter Plot on Total Sulfur Dioxide in Log Scale and Fixed Acidity,\
          Colored by pH Value") + 
  xlab("Fixed Acidity Level (g/dm^3)") +
  ylab("Total Sulfur Dioxide Level in Log Scale (mg/dm^3)") +
  theme(plot.title = element_text(hjust = 0.5))

grid.arrange(acidScatterPlot1, acidScatterPlot2, acidScatterPlot3)
```

### Description Two
The combination of the three acidic features against the fixed.acidity, coloured
by the pH value indicated that an interesting fact that the pH value of the wine
is dominated by fixed.acidity. All other acidic chemicals seems to have no 
significant impact on pH value. That make a lot of sense in terms of chemistry. 
total.sulfur.dioxide are in a degree of mg/dm^3 while all other acidic fields 
looking at citric acid, volatile acidity and fixed acidity, citric acid and 
volatile acid are in the degree of 10^-1 g/dm^3 while fixed.acidity is in the 
degree of 10^1 g/dm3. Assuming that they have less than 100 times of molarity 
differences, fixed acidity will have a absolute impact on acidity. But more 
interestingly is that, volatile acidity is contributing so much on the quality 
score. After some research on wikipedia, the reason is that acetic acid has a 
distinctive pungent smell, and in fact a main component of vineger.

### Plot Three
```{r echo=FALSE, Plot_Three}
ggplot(aes(x = alcohol, y = volatile.acidity, color = quality.factor),
       data=redWineData) +
  geom_point() +
  ggtitle("Scatter Plot on Volatile Acidity and Alcohol Level,\
          Colored by Quality Score") + 
  xlab("Alcohol Level (% by volume)") +
  ylab("Volatile Acidity (g/dm^3)") +
  labs(color='Wine Quality') +
  scale_colour_brewer(type = "seq", palette = 2) +
  theme_dark() +
  theme(plot.title = element_text(hjust = 0.5))
```

### Description Three
This plot is showing the relationship between the two main features and the 
quality. This plot proved our thought that alcohol and volatile.acidity can 
predict the wine quality. We ended up with a mathematical model of 
quality = 0.31381 * alcohol - 1.38364 * volatile.acidity + 3.09547 which are 
able to predict more than 75% of our data with less than 0.5 absolute error 
in quality.

------

# Reflection

This red wine dataset is a pretty small dataset with only 1599 observations. 
However, there were a lot that could be investigated with these 12 variables. 
I first tried to plot a histogram of all variable to understand the overview 
of the data first and that went quite well. However this doesn't helped me in 
identifying the features that we related to quality. This need to be done in 
bivariate analysis. All the important features that I identified in univariate 
analysis section turns out to be not really meaningful, while a variable I 
ignored (alcohol) turns out to be very important.

I was also surprised that a lot of factors that might seems important to a lot 
of people like sweetness, are not that important in experts' eye. At the same 
time, alcohol level seemed to be not that important in terms of quality was 
extremely imprtant predictor.

The model and investigations that I did in this project is based on considering 
the vairables as individual features, i.e. we didn't really develop new features
by combining multiple features. Thus, the model is too simple to give an 
accurate prediction. According to the R^2 score, only less than 40% of the 
variance of the quality is explained by this simple model.

To further work on this dataset, we should employ more advanced machine learning
techniques. Algorithms like neural network are better at combining multiple 
features and come up with comprehensive mathematical model. These models can 
also take more factors into considerations.
